Neural Network Language Models for Automatic Speech Recognition

### 2018-12-12 paper/paper.tex
paper: Fix some typos

Prior to the introduction of RNNs, most language models used n-grams
in Hidden Markov Model chains, where it was assumed that the $k$th
word depended only on the prior $n$ words. One key problem
with this model is that the context window is of a fixed size, leading
to a horizon problem. The Horizon problem occur because a if there were a word
in the word sequence which is extremely predictive of the $(n + 1)$th
word away from the current word, that would would simply not be taken
into account in that model. Worse still, the fixed size context window
means that unnecessary weight is put on words that happen to be in the context
window that may actually not be all that predictive were the context window
infinite.

@@

The second dataset we used was Gigaword. This dataset is based on XXX,
containing 8,658,023 tokens in the training set, and 341,317 tokens in the
validation set. The combined dictionary contains 59760 unique tokens.

"five time world champion kwan withdrew from the US figure skating championships
on Wednesday, but will petition US skating officials for the chance to compete
\emph{at the Turin Olympics}."

"US business leaders lashed out wednesday at legislation that would penalize companies
\emph{for employing illegal immigrants}."

@@

$$ WER = \frac{S + D + I}{N} $$, where $N$ is the number of
words and $S, D, I$ are substitutions, deletions, insertions.
This is similar to the Levenstein distance between documents.

>>>>

Prior to the introduction of RNNs, most language models used n-grams
in Hidden Markov Model chains, where it was assumed that the $k$th
word depended only on the prior $n$ words. One key problem
with this model is that the context window is of a fixed size, leading
to a horizon problem. The horizon problem occurs because a if there were a word
in the word sequence which is extremely predictive of the $(n + 1)$th
word away from the current word, that word would simply not be taken
into account in that model. Worse still, the fixed size context window
means that unnecessary weight is put on words that happen to be in the context
window that may actually not be all that predictive were the context window
infinite.

@@

The second dataset we used was Gigaword. This dataset is based on news articles,
containing 8,658,023 tokens in the training set, and 341,317 tokens in the
validation set. The combined dictionary contains 59760 unique tokens.

Samples from the Dataset include (expected predictions highlighted):

"five time world champion Kwan withdrew from the US figure skating championships
on Wednesday, but will petition US skating officials for the chance to compete
\emph{at the Turin Olympics}."

"US business leaders lashed out Wednesday at legislation that would penalize companies
\emph{for employing illegal immigrants}."

@@

$$ WER = \frac{S + D + I}{N} $$, where $N$ is the number of
words and $S, D, I$ are substitutions, deletions, insertions.
This is similar to the Levensteihn distance between documents.
